Eye in a Disk: eyeIntegration human pan-eye and body transcriptome database version 1.0

### 2019-06-03 manuscript.Rmd
remove mgs from tsne plot

tsne_50 <- tsne_50 %>% filter(Tissue != 'Choroid Plexus', !(Tissue == 'Retina' & X2 > 20))
dbscan_cluster <- dbscan(tsne_50 %>% select(X1, X2),  minPts = 3, eps = 2.5)
tsne_50$Cluster <- dbscan_cluster$cluster
col1 = 'X1'
col2 = 'X2'
# create label points for each cluster
cluster_centers <- tsne_50 %>%
  left_join(.,core_tight_2019) %>% group_by(Cluster) %>%
  summarise(C1=mean(!!sym(col1)),C2=mean(!!sym(col2)),Tissue=paste(unique(Tissue),collapse=','))

@@

```{r mapping_rate, echo = F, message = F,  warning=F, fig.height = 4, fig.width = 10, fig.pos='H', fig.cap = mapping_rate_cap}
mapping_rate <- read_delim('data/mapping_rate.txt', delim = ' ', col_names = F) %>% 
  mutate(X2 = str_sub(X2, 1, 4) %>% as.numeric()) %>%  
  rename(sample_accession = X1, `Mapping Rate` = X2)
mapping_stats <- core_tight_2019 %>% left_join(mapping_rate) %>% pull(`Mapping Rate`) %>% summary() %>% broom::tidy()
mapping_rate_cap <- supFig_cap(name='mapping_rate_cap', caption = paste0('Salmon mapping rate for each sample, grouped by tissue type. 1st quartile mapping rate is ', mapping_stats$q1, '%, median is ', mapping_stats$median, '%, mean is ', mapping_stats$mean, '%, and third quartile is ', mapping_stats$q3, '%.'))
core_tight_2019 %>% 
  left_join(mapping_rate, by = 'sample_accession') %>% 
  ggplot(aes(x=Tissue, y = `Mapping Rate`)) + 
  ggbeeswarm::geom_quasirandom() + 
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + coord_cartesian(ylim=c(0,100))

>>>>

tsne_50 <- tsne_50 %>% filter(Tissue != 'Choroid Plexus', !grepl('MGS', Sub_Tissue))
dbscan_cluster <- dbscan(tsne_50 %>% select(X1, X2),  minPts = 3, eps = 2.5)
tsne_50$Cluster <- dbscan_cluster$cluster
col1 = 'X1'
col2 = 'X2'
# create label points for each cluster
cluster_centers <- tsne_50 %>%
  left_join(.,core_tight_2019) %>% group_by(Cluster) %>%
  summarise(C1=mean(!!sym(col1)),C2=mean(!!sym(col2)),Tissue=paste(unique(Tissue),collapse=','))

@@

```{r mapping_rate, echo = F, message = F,  warning=F, fig.height = 4, fig.width = 10, fig.pos='H', fig.cap = mapping_rate_cap}
mapping_rate <- read_delim('data/mapping_rate.txt', delim = ' ', col_names = F) %>% 
  mutate(X2 = str_sub(X2, 1, 4) %>% as.numeric()) %>%  
  rename(sample_accession = X1, `Mapping Rate` = X2)
mapping_stats <- core_tight_2019 %>% left_join(mapping_rate) %>% pull(`Mapping Rate`) %>% summary() %>% broom::tidy()
mapping_rate_cap <- supFig_cap(name='mapping_rate_cap', caption = paste0('Salmon mapping rate for each sample, grouped by tissue type. 1st quartile mapping rate is ', mapping_stats$q1, '%, median is ', mapping_stats$median, '%, mean is ', mapping_stats$mean, '%, and third quartile is ', mapping_stats$q3, '%.'))
core_tight_2019 %>% 
  left_join(mapping_rate, by = 'sample_accession') %>% 
  mutate(Tissue = case_when(grepl('MGS', Sub_Tissue) ~ 'Retina MGS',
                            TRUE ~ Tissue)) %>% 
  ggplot(aes(x=Tissue, y = `Mapping Rate`)) + 
  ggbeeswarm::geom_quasirandom() + 
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + coord_cartesian(ylim=c(0,100))
